A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-27 UAM2014/Article/article.tex
la2pdf commit - 2014:04:27	23:31:47	(Sun27.Apr)

To produce the sonar templates we assume rough, isotropic surface that reflects energy equally in all directions. This well with a Lambertian scattering model where the backscatter intensity depends only on the angle between the incident angle and surface normal.

@@

\begin{itemize}
\item Lambertian surface scattering model. Rough, isotropic, reflects energy equally in all directions. Intensity depends only on the angle between the look direction and surface normal.
\item 
\end{itemize}

@@

\begin{figure}[t]\centering%
\begin{subfigure}[b]{.5\linewidth-0.5cm}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{cutmean}%
\end{subfigure}\hspace{1cm}%
\begin{subfigure}[b]{.5\linewidth-0.5cm}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{cutmean}%
\end{subfigure} 
\end{figure}

>>>>

To produce the sonar templates we assume a rough, isotropic surface that reflects energy equally in all directions. This permits us to use a Lambertian scattering model where the backscatter intensity depends only on the incidence angle~\cite{Zhang1999}. It does not consider observation angle or sound frequency\todo{is this unproblematic?}.

@@

@@

\begin{figure}[t]\centering%
\begin{subfigure}[b]{.5\linewidth-0.5cm}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{cutmean}%
\end{subfigure}\hspace{1cm}%
\begin{subfigure}[b]{.5\linewidth-0.5cm}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged_bw.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{cutmean}%
\end{subfigure} 
\end{figure}
